Appendix 4: Model Comparison Code For Manuscript

### 2025-10-30 modelcomparison_code.Rmd
Adding labels to figure

pf <- data.forest %>% 
  ggplot(aes(est,xmin=ci.lower,xmax=ci.upper,y=term,fill=hollow_group,color=color,linetype=linetype))+
  geom_vline(xintercept=0,color="grey") +
  geom_linerange(aes(size = sample), position=pos) +
  scale_size_manual(values = c("Australia" = 1.2, "Finland" = 0.8)) +
  geom_point(aes(shape = sample),size=3,position=pos,alpha=0.7)+
  scale_fill_discrete(na.value=NA, guide ="none") + 
  labs(x="Standardised Effect Size",y="Relationship") +
  labs(color="Model type", linetype="Variable type", shape="Sample") + 
  guides(size = "none") +
  geom_stripped_rows(color=NA) + theme_classic()

>>>>

pf <- data.forest %>% 
  ggplot(aes(est,xmin=ci.lower,xmax=ci.upper,y=term,fill=hollow_group,color=color,linetype=linetype))+
  geom_vline(xintercept=0,color="grey") +
  geom_linerange(aes(size = sample), position=pos) +
  scale_size_manual(values = c("Australia" = 1.2, "Finland" = 0.8)) +
  geom_point(aes(shape = sample),size=3,position=pos,alpha=0.7)+
  scale_fill_discrete(na.value=NA, guide ="none") + 
  scale_y_discrete(
    name = "Relationship", 
    labels = c(
      "ind_eff2:ind_eff2:=a2*b2" = "Indirect Effect: a2*b2", 
      "ind_eff1:ind_eff1:=a1*b1" = "Indirect Effect: a1*b1",
      "ind_eff:=a1*d21*b2" = "Indirect Effect: a1*d21*b1",
      "d21:selfid~psycown" = "Identity*Ownership (d21)",
      "cp:intention~donation" = "Intention*Donation (cp)",
      "b2:intention~selfid" = "Intention*Identity (b2)",
      "b1:intention~psycown" = "Intention*Owenrship (b1)",
      "a2:selfid~donation" = "Identity*Donation (a2)",
      "a1:psycown~donation" = "Ownership*Donation(a1)"
    )
  ) +
  labs(x="Standardised Effect Size",y="Relationship") +
  labs(color="Model type", linetype="Variable type", shape="Sample") + 
  guides(size = "none") +
  geom_stripped_rows(color=NA) + theme_classic()
